---
title: "RAMDOM FOREST - WATERHEMP"
author: "Felipe A. Faleco"
date: "03/11/2021"
output: pdf_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(parsnip)
library(tidymodels)
library(vctrs)
library(hardhat)
library(tidyverse)
library(ggplot2)
library(RColorBrewer)
library(tidyr)
library(doParallel)
library(ranger)
library(vip)
library(tuneRanger)
library(mlr)

```


# DATA

```{r}

data <- read.csv("RANDOM FOREST_FINAL.csv")

```




# IMAZETHAPYR

```{r}

ima_data <- data %>% 
  filter(herb == "imazethapyr") %>% 
  select(ima_R, SOA_1, SOA_2, SOA_4, SOA_5, SOA_6, SOA_9, SOA_10, SOA_14, SOA_15, SOA_19, SOA_27) %>% 
  mutate_if(is.character, as.factor)
  
str(ima_data)

```


## DATA SAMPLING

```{r}

# SEPARATE DATA INTO TRAINING (3/4) AND TESTING (1/4) SET. 

ima_split <- initial_split(ima_data)

ima_split %>%
  training() %>%
  glimpse()

ima_split %>%
  testing() %>%
  glimpse()

```



## PRE-PROCESSING

```{r}

ima_recipe <- training(ima_split) %>%
  recipe(ima_R ~ .) %>%
  prep()

ima_recipe

```


## EXECUTE PRE-PROCESSING

```{r}

# LOAD PREPARED TESTING DATA

ima_testing <- ima_recipe %>%
  bake(testing(ima_split)) 

glimpse(ima_testing)



# LOAD PREPARED TRAINING DATA

ima_training <- juice(ima_recipe)

glimpse(ima_training)


```


## MODEL TUNNING

```{r}

ima_task <- makeClassifTask(data = ima_data, target = "ima_R")

estimateTimeTuneRanger(ima_task)

ima_tuneRanger <- tuneRanger(ima_task, measure = list(auc), num.trees = 1000, num.threads = 2, iters = 70, iters.warmup = 30)

ima_tuneRanger

```



## MODEL TRAINING

```{r}

ima_ranger <- rand_forest(trees = 1000, mtry = 6, min_n = 5, mode = "classification") %>%
  set_engine("ranger", importance ="permutation") %>%
  fit(ima_R ~ ., data = ima_training)

ima_ranger

```



## PREDICTIONS

```{r}

ima_ranger %>%
  predict(ima_testing) %>%
  bind_cols(ima_testing) %>%
  glimpse()

```


## MODEL VALIDATIONS

```{r}

ima_ranger %>%
  predict(ima_testing) %>%
  bind_cols(ima_testing) %>%
  metrics(truth = ima_R, estimate = .pred_class)

```


## PLOT

```{r}

ima_ranger %>%
  vip(geom = "col", horizontal = TRUE, aesthetics = list(fill = "darkred", width = 0.5)) +
  labs(title = "Random Forest - Imazethapyr POST", x = "Variable", y = "Importance") + 
  theme_bw() + 
  theme(plot.title = element_text(face = "bold", hjust = 0.5, size = 20, colour = "darkgreen"), 
         axis.title = element_text(face = "bold", size = 16, colour = "darkgreen"), 
         axis.text = element_text(face = "bold", size = 14, colour = "black"))

```




# GLYPHOSATE

```{r}

gly_data <- data %>% 
  filter(herb == "glyphosate") %>% 
  select(gly_R, SOA_1, SOA_2, SOA_4, SOA_5, SOA_6, SOA_9, SOA_10, SOA_14, SOA_15, SOA_19, SOA_27) %>% 
  mutate_if(is.character, as.factor)
  
str(gly_data)

```


## DATA SAMPLING

```{r}

# SEPARATE DATA INTO TRAINING (3/4) AND TESTING (1/4) SET. 

gly_split <- initial_split(gly_data)

gly_split %>%
  training() %>%
  glimpse()

gly_split %>%
  testing() %>%
  glimpse()

```



## PRE-PROCESSING

```{r}

gly_recipe <- training(gly_split) %>%
  recipe(gly_R ~ .) %>%
  prep()

gly_recipe

```


## EXECUTE PRE-PROCESSING

```{r}

# LOAD PREPARED TESTING DATA

gly_testing <- gly_recipe %>%
  bake(testing(gly_split)) 

glimpse(gly_testing)



# LOAD PREPARED TRAINING DATA

gly_training <- juice(gly_recipe)

glimpse(gly_training)


```


## MODEL TUNNING

```{r}

gly_task <- makeClassifTask(data = gly_data, target = "gly_R")

estimateTimeTuneRanger(gly_task)

gly_tuneRanger <- tuneRanger(gly_task, measure = list(auc), num.trees = 1000, num.threads = 2, iters = 70, iters.warmup = 30)

gly_tuneRanger

```



## MODEL TRAINING

```{r}

gly_ranger <- rand_forest(trees = 1000, mtry = 11, min_n = 11, mode = "classification") %>%
  set_engine("ranger", importance ="permutation") %>%
  fit(gly_R ~ ., data = gly_training)

gly_ranger

```



## PREDICTIONS

```{r}

gly_ranger %>%
  predict(gly_testing) %>%
  bind_cols(gly_testing) %>%
  glimpse()

```


## MODEL VALIDATIONS

```{r}

gly_ranger %>%
  predict(gly_testing) %>%
  bind_cols(gly_testing) %>%
  metrics(truth = gly_R, estimate = .pred_class)

```


## PLOT

```{r}

gly_ranger %>%
  vip(geom = "col", horizontal = TRUE, aesthetics = list(fill = "darkred", width = 0.5)) +
  labs(title = "Random Forest - Glyphosate POST", x = "Variable", y = "Importance") + 
  theme_bw() + 
  theme(plot.title = element_text(face = "bold", hjust = 0.5, size = 20, colour = "darkgreen"), 
         axis.title = element_text(face = "bold", size = 16, colour = "darkgreen"), 
         axis.text = element_text(face = "bold", size = 14, colour = "black"))

```




# ATRAZINE

```{r}

atra_data <- data %>% 
  filter(herb == "atrazine") %>% 
  select(atra_R, SOA_1, SOA_2, SOA_4, SOA_5, SOA_6, SOA_9, SOA_10, SOA_14, SOA_15, SOA_19, SOA_27) %>% 
  mutate_if(is.character, as.factor)
  
str(atra_data)

```


## DATA SAMPLING

```{r}

# SEPARATE DATA INTO TRAINING (3/4) AND TESTING (1/4) SET. 

atra_split <- initial_split(atra_data)

atra_split %>%
  training() %>%
  glimpse()

atra_split %>%
  testing() %>%
  glimpse()

```



## PRE-PROCESSING

```{r}

atra_recipe <- training(atra_split) %>%
  recipe(atra_R ~ .) %>%
  prep()

atra_recipe

```


## EXECUTE PRE-PROCESSING

```{r}

# LOAD PREPARED TESTING DATA

atra_testing <- atra_recipe %>%
  bake(testing(atra_split)) 

glimpse(atra_testing)



# LOAD PREPARED TRAINING DATA

atra_training <- juice(atra_recipe)

glimpse(atra_training)


```


## MODEL TUNNING

```{r}

atra_task <- makeClassifTask(data = atra_data, target = "atra_R")

estimateTimeTuneRanger(atra_task)

atra_tuneRanger <- tuneRanger(atra_task, measure = list(auc), num.trees = 1000, num.threads = 2, iters = 70, iters.warmup = 30)

atra_tuneRanger

```



## MODEL TRAINING

```{r}

atra_ranger <- rand_forest(trees = 1000, mtry = 10, min_n = 25, mode = "classification") %>%
  set_engine("ranger", importance ="permutation") %>%
  fit(atra_R ~ ., data = atra_training)

atra_ranger

```



## PREDICTIONS

```{r}

atra_ranger %>%
  predict(atra_testing) %>%
  bind_cols(atra_testing) %>%
  glimpse()

```


## MODEL VALIDATIONS

```{r}

atra_ranger %>%
  predict(atra_testing) %>%
  bind_cols(atra_testing) %>%
  metrics(truth = atra_R, estimate = .pred_class)

```


## PLOT

```{r}

atra_ranger %>%
  vip(geom = "col", horizontal = TRUE, aesthetics = list(fill = "darkred", width = 0.5)) +
  labs(title = "Random Forest - Atrazine POST", x = "Variable", y = "Importance") + 
  theme_bw() + 
  theme(plot.title = element_text(face = "bold", hjust = 0.5, size = 20, colour = "darkgreen"), 
         axis.title = element_text(face = "bold", size = 16, colour = "darkgreen"), 
         axis.text = element_text(face = "bold", size = 14, colour = "black"))

```
