---
title: "RAMDOM FOREST - WATERHEMP"
author: "Felipe A. Faleco"
date: "03/11/2021"
output: pdf_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(parsnip)
library(tidymodels)
library(vctrs)
library(hardhat)
library(tidyverse)
library(ggplot2)
library(RColorBrewer)
library(tidyr)
library(doParallel)
library(ranger)
library(vip)

```


# DATA

```{r}

data <- read.csv("RANDOM FOREST.csv")

```




# IMAZETHAPYR

```{r}

ima_data <- data %>% 
  filter(herb == "imazethapyr") %>% 
  select(ima_R, County, Tillage, Manure, SOA_2) %>%
  mutate_if(is.character, as.factor)
  
str(ima_data)

```


## SPLITING

```{r}

set.seed(123)

ima_split <- initial_split(ima_data, strata = ima_R)

ima_train <- training(ima_split)

ima_test <- testing(ima_split)

```



## RECIPE

```{r}

ima_recipe <- recipe(ima_R ~ ., data = ima_train)

```



## MODEL

```{r}

ima_model <- rand_forest(mtry = tune(), trees = 1000, min_n = tune()) %>% 
  set_mode("classification") %>%
  set_engine("ranger")

```



## WORKFLOW

```{r}

ima_workflow <- workflow() %>%
  add_recipe(ima_recipe) %>% 
  add_model(ima_model) 

```



## RANDOMLY PERMUTTING EXPLANATORY VARIABLES

```{r}

set.seed(456)

ima_vfold_cv <- vfold_cv(ima_train)

#doParallel::registerDoParallel() 

set.seed(345)

ima_tune_grid <- tune_grid(ima_workflow, resamples = ima_vfold_cv, grid = 20) 

```


## CHECK BEST MTRY & MIN.N SUGGESTED

```{r}

ima_tune_grid %>% select_best("accuracy")

ima_tune_grid %>%
  collect_metrics() %>% 
  filter(.metric =="accuracy") %>% 
  pivot_longer(min_n:mtry, values_to="value", names_to="parameter") %>% 
  ggplot(aes(value, mean, color=parameter)) +
  geom_point(show.legend=FALSE) +
  facet_wrap(~ parameter)

```


## REFINE MTRY & MIN.N 

```{r}

ima_grid_reg <- grid_regular(mtry(range = c(0,5)), min_n(range = c(5,40)), levels = 5) 


set.seed(456)
ima_tune_grid_ref <- tune_grid(ima_workflow, resamples = ima_vfold_cv, grid = ima_grid_reg)

```


## CHECK MTRY & MIN.N REFINED

```{r}

ima_tune_grid_ref %>% select_best("accuracy")


ima_tune_grid_ref %>%
  collect_metrics() %>%
  filter(.metric =="accuracy") %>% 
  mutate(min_n = factor(min_n)) %>% 
  ggplot(aes(mtry, mean, color = min_n)) +
  geom_line(alpha = 0.5, size = 1.5) +
  geom_point()

```



## FINALIZE MODEL

```{r}

ima_best_accuracy <- select_best(ima_tune_grid_ref, "accuracy")

ima_best_accuracy

ima_final_model <- finalize_model(ima_model, ima_best_accuracy)

```



## PLOT 
```{r}

ima_final_model %>%
  set_engine("ranger", importance ="impurity") %>% 
  fit(ima_R ~ ., data = ima_train) %>%
  vip(geom = "col", horizontal = TRUE, aesthetics = list(fill = "darkred", width = 0.5)) +
  labs(title = "Random Forest - Imazethapyr POST", x = "Variable", y = "Importance") + 
  theme_bw() + 
  theme(plot.title = element_text(face = "bold", hjust = 0.5, size = 20, colour = "darkgreen"), 
         axis.title = element_text(face = "bold", size = 16, colour = "darkgreen"), 
         axis.text = element_text(face = "bold", size = 14, colour = "black")) +
  ggsave("RANDOMFOREST_IMA.jpeg", units = "in", width = 6, height = 4, dpi = 600)

```


## CHECKING THE MODEL

```{r}

ima_workflow_final <- workflow() %>%
  add_recipe(ima_recipe) %>%
  add_model(ima_final_model)

ima_final_res <- ima_workflow_final %>%
  last_fit(ima_split)

ima_final_res %>%
  collect_metrics()

ima_final_res %>%
  collect_predictions() %>% 
  bind_cols(ima_test)

```



# GLYPHOSATE

```{r}

gly_data <- data %>% 
  filter(herb == "glyphosate") %>% 
  select(gly_R, County, Tillage, Manure, SOA_9) %>%
  mutate_if(is.character, as.factor)
  
str(gly_data)

```


## SPLITING

```{r}

set.seed(123)

gly_split <- initial_split(gly_data, strata = gly_R)

gly_train <- training(gly_split)

gly_test <- testing(gly_split)

```



## RECIPE

```{r}

gly_recipe <- recipe(gly_R ~ ., data = gly_train)

```



## MODEL

```{r}

gly_model <- rand_forest(mtry = tune(), trees = 1000, min_n = tune()) %>% 
  set_mode("classification") %>%
  set_engine("ranger")

```



## WORKFLOW

```{r}

gly_workflow <- workflow() %>%
  add_recipe(gly_recipe) %>% 
  add_model(gly_model) 

```



## RANDOMLY PERMUTTING EXPLANATORY VARIABLES

```{r}

set.seed(456)

gly_vfold_cv <- vfold_cv(gly_train)

#doParallel::registerDoParallel() 

set.seed(345)

gly_tune_grid <- tune_grid(gly_workflow, resamples = gly_vfold_cv, grid = 20) 

```


## CHECK BEST MTRY & MIN.N SUGGESTED

```{r}

gly_tune_grid %>% select_best("accuracy")

gly_tune_grid %>%
  collect_metrics() %>% 
  filter(.metric =="accuracy") %>% 
  pivot_longer(min_n:mtry, values_to="value", names_to="parameter") %>% 
  ggplot(aes(value, mean, color=parameter)) +
  geom_point(show.legend=FALSE) +
  facet_wrap(~ parameter)

```


## REFINE MTRY & MIN.N 

```{r}

gly_grid_reg <- grid_regular(mtry(range = c(0,5)), min_n(range = c(5,40)), levels = 5) 


set.seed(456)
gly_tune_grid_ref <- tune_grid(gly_workflow, resamples = gly_vfold_cv, grid = gly_grid_reg)

```


## CHECK MTRY & MIN.N REFINED

```{r}

gly_tune_grid_ref %>% select_best("accuracy")


gly_tune_grid_ref %>%
  collect_metrics() %>%
  filter(.metric =="accuracy") %>% 
  mutate(min_n = factor(min_n)) %>% 
  ggplot(aes(mtry, mean, color = min_n)) +
  geom_line(alpha = 0.5, size = 1.5) +
  geom_point()

```



## FINALIZE MODEL

```{r}

gly_best_accuracy <- select_best(gly_tune_grid_ref, "accuracy")

gly_best_accuracy

gly_final_model <- finalize_model(gly_model, gly_best_accuracy)

```



## PLOT 
```{r}

gly_final_model %>%
  set_engine("ranger", importance ="impurity") %>% 
  fit(gly_R ~ ., data = gly_train) %>%
  vip(geom = "col", horizontal = TRUE, aesthetics = list(fill = "darkred", width = 0.5)) +
  labs(title = "Random Forest - Glyphosate POST", x = "Variable", y = "Importance") + 
  theme_bw() + 
  theme(plot.title = element_text(face = "bold", hjust = 0.5, size = 20, colour = "darkgreen"), 
         axis.title = element_text(face = "bold", size = 16, colour = "darkgreen"), 
         axis.text = element_text(face = "bold", size = 14, colour = "black")) +
  ggsave("RANDOMFOREST_GLY.jpeg", units = "in", width = 6, height = 4, dpi = 600)

```


## CHECKING THE MODEL

```{r}

gly_workflow_final <- workflow() %>%
  add_recipe(gly_recipe) %>%
  add_model(gly_final_model)

gly_final_res <- gly_workflow_final %>%
  last_fit(gly_split)

gly_final_res %>%
  collect_metrics()

gly_final_res %>%
  collect_predictions() %>% 
  bind_cols(gly_test)

```



# ATRAZINE

```{r}

atra_data <- data %>% 
  filter(herb == "atrazine") %>% 
  select(atra_R, County, Tillage, Manure, SOA_5) %>%
  mutate_if(is.character, as.factor)
  
str(atra_data)

```


## SPLITING

```{r}

set.seed(123)

atra_split <- initial_split(atra_data, strata = atra_R)

atra_train <- training(atra_split)

atra_test <- testing(atra_split)

```



## RECIPE

```{r}

atra_recipe <- recipe(atra_R ~ ., data = atra_train)

```



## MODEL

```{r}

atra_model <- rand_forest(mtry = tune(), trees = 1000, min_n = tune()) %>% 
  set_mode("classification") %>%
  set_engine("ranger")

```



## WORKFLOW

```{r}

atra_workflow <- workflow() %>%
  add_recipe(atra_recipe) %>% 
  add_model(atra_model) 

```



## RANDOMLY PERMUTTING EXPLANATORY VARIABLES

```{r}

set.seed(456)

atra_vfold_cv <- vfold_cv(atra_train)

#doParallel::registerDoParallel() 

set.seed(345)

atra_tune_grid <- tune_grid(atra_workflow, resamples = atra_vfold_cv, grid = 20) 

```


## CHECK BEST MTRY & MIN.N SUGGESTED

```{r}

atra_tune_grid %>% select_best("accuracy")

atra_tune_grid %>%
  collect_metrics() %>% 
  filter(.metric =="accuracy") %>% 
  pivot_longer(min_n:mtry, values_to="value", names_to="parameter") %>% 
  ggplot(aes(value, mean, color=parameter)) +
  geom_point(show.legend=FALSE) +
  facet_wrap(~ parameter)

```


## REFINE MTRY & MIN.N 

```{r}

atra_grid_reg <- grid_regular(mtry(range = c(0,5)), min_n(range = c(25,40)), levels = 5) 


set.seed(456)
atra_tune_grid_ref <- tune_grid(atra_workflow, resamples = atra_vfold_cv, grid = atra_grid_reg)

```


## CHECK MTRY & MIN.N REFINED

```{r}

atra_tune_grid_ref %>% select_best("accuracy")


atra_tune_grid_ref %>%
  collect_metrics() %>%
  filter(.metric =="accuracy") %>% 
  mutate(min_n = factor(min_n)) %>% 
  ggplot(aes(mtry, mean, color = min_n)) +
  geom_line(alpha = 0.5, size = 1.5) +
  geom_point()

```



## FINALIZE MODEL

```{r}

atra_best_accuracy <- select_best(atra_tune_grid_ref, "accuracy")

atra_best_accuracy

atra_final_model <- finalize_model(atra_model, atra_best_accuracy)

```



## PLOT 
```{r}

atra_final_model %>%
  set_engine("ranger", importance ="impurity") %>% 
  fit(atra_R ~ ., data = atra_train) %>%
  vip(geom = "col", horizontal = TRUE, aesthetics = list(fill = "darkred", width = 0.5)) +
  labs(title = "Random Forest - Atrazine POST", x = "Variable", y = "Importance") + 
  theme_bw() + 
  theme(plot.title = element_text(face = "bold", hjust = 0.5, size = 20, colour = "darkgreen"), 
         axis.title = element_text(face = "bold", size = 16, colour = "darkgreen"), 
         axis.text = element_text(face = "bold", size = 14, colour = "black")) +
  ggsave("RANDOMFOREST_ATRA.jpeg", units = "in", width = 6, height = 4, dpi = 600)

```


## CHECKING THE MODEL

```{r}

atra_workflow_final <- workflow() %>%
  add_recipe(atra_recipe) %>%
  add_model(atra_final_model)

atra_final_res <- atra_workflow_final %>%
  last_fit(atra_split)

atra_final_res %>%
  collect_metrics()

atra_final_res %>%
  collect_predictions() %>% 
  bind_cols(atra_test)

```

